---
title: "p8105_hw1_yw3439"
author: "Qetsiyah Wang"
date: "9/17/2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
```

## Problem.1 - Data frome and Variable
```{r}

frame_x = tibble(
  sample_x = rnorm(10),
  logi_vec = sample_x > 0,
  subj_char = c("math", "english", "history", "chinese", "science", "biology", 
               "politics", "geography", "physics", "chemistry"),
  county_fac = as.factor(c("Manhattan","Manhattan","Manhattan","Manhattan", 
                        "Queen", "Queen", "Queen",
                        "Bronx", "Bronx", "Bronx"))
)

mean_frame = tibble(
  mean_sample = mean(pull(frame_x, sample_x)),
  mean_logi = mean(pull(frame_x, logi_vec)),
  mean_char = mean(pull(frame_x, subj_char)),
  mean_fac = mean(pull(frame_x, county_fac))
)

```
  In the data frame x, sample_x is numeric containing random numbers from a standard distribution. logi_vec contains boolean statements from identifying if the vector in sample_x is bigger than 0. subj_char consists of subjects as character vectors. county_fac has 10 vectors with 3 different factor levels "Manhattan", "Queen" and "Bronx". While taking the mean for each variable, there is a warning coming up showing that argument is not numeric or logical so that returning NA. Shown in the data frame of mean_frame, only sample_x and logi_vec show mean results but not subj_char and county_fac, because vectors in subj_vec are characters and in county_fac are factors, which both cannot be applied with the mean function.
  
```{r, include=False}

frame_x %>%
  mutate(
    logi_vec = as.numeric(logi_vec),
    subj_char = as.numeric(subj_char),
    county_fac = as.numeric(county_fac)
  )

```
  



```{r}

frame_x %>%
  mutate(
    num_logi = (as.numeric(logi_vec))*sample_x,
    fac_logi = (as.factor(logi_vec))*sample_x,
    num_fac_logi = (as.factor(as.numeric(logi_vec)))*sample_x
  )

```







